### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on tank treading

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
The four marker points are the Lagrangian points where the tank-treading
velocities are computed, the black dashed line is the center line of the
channel, and the rounded arrow denotes the direction of rotation. The
stiff single-component and multicomponent vesicles are clearly tank
treading. The direction and speed of the tank-treading depends on the
how much of the vesicle membrane is exposed to positive shear (below the
center line) versus how much is exposed to negative shear (above the
center line). The majority of the membrane of the stiff single-component
and multicomponent vesicles are below the center line, and this results
in a clockwise tank-treading behavior. In contrast, the majority of the
membrane of the floppy single-component vesicle is above the center
line, and the result is counterclockwise tank-treading. In addition, the
tank-treading velocity can be correlated to the percentage of its
membrane that is below the center line. We note, however, that the
floppy single-component vesicle is still undergoing deformations, so the
tangential velocities have not converged to a fixed value.

>>>>

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
Figure~\ref{fig:lubricationComposite} are the tank-treading velocities
of four Lagrangian points. The inset shows the vesicle configuration in
the closely-fitting part of the channel, the black dashed line is the
center line of the channel, and the rounded arrow denotes the direction
of rotation. The stiff single-component and multicomponent vesicles are
clearly tank treading. The direction and speed of the tank-treading
depends on the how much of the vesicle membrane is exposed to positive
shear (below the center line) versus how much is exposed to negative
shear (above the center line). The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise tank-treading. In
addition, the tank-treading velocity can be correlated to the percentage
of its membrane that is below the center line. We note, however, that
the floppy single-component vesicle is still undergoing deformations, so
the tangential velocities have not converged to a fixed value.
